The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types

### 2023-05-27 final/paper/main.tex
update

  First, preprocess the dataset, e.g. normalize, apply PCA, apply AE. Second, classify the data after preprocessing. 
  With this step the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
  be varied depending on the classification algorithm. For KNN, the criterion is distance and probability. More specifically, 
  assume a data point $x$, and the k-nearest data points are $p_1,...,p_k$. Only those points whose distance between 
  $x$ smaller than $L$ will be marked valid. Denote the valid data points as $p'_1,...p'_n$, and the corresponding 
  labels are $l_1,...,l_n$. If this data point satisifies Eq~\ref{eqn:KNN_prob}, mark it as unkown type.
  \begin{equation}
    \label{eqn:KNN_prob}
    \frac{\arg\max_{t\in\text{types}\{N(t)\}}}{n}<P
  \end{equation}
  where $P$ is a manunally set probability and $N(t)$ is the number of type $t$ in those $n$ valid data points.

@@

@@

  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
    \caption{An example that multiple SVMs fail}
    \label{fig:SVM_fail}
  \end{figure}
  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\     
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $X$               & $X$        & $X$                   & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $X$               & $X$        & $X$                   & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

>>>>

  First, preprocess the dataset, e.g. normalize, apply PCA, apply AE. Second, classify the data after preprocessing. 
  In the experiment, we use PCA and AE to reduce the dimension down to 32 and 30 in arrhythmia dataset and gene 
  expression cancer RNA-Seq dataset, respectively. 
  With this step, the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
  be varied depending on the classification algorithm. For KNN, the criterion is distance and probability. More specifically, 
  assume a data point $x$, and the k-nearest data points are $p_1,...,p_k$. Only those points whose distance between 
  $x$ smaller than $L$ will be marked valid. Denote the valid data points as $p'_1,...p'_n$, and the corresponding 
  labels are $l_1,...,l_n$. If this data point satisifies Eq~\ref{eqn:KNN_prob}, mark it as unkown type.
  \begin{equation}
    \label{eqn:KNN_prob}
    \frac{\arg\max_{t\in\text{types}\{N(t)\}}}{n}<P
  \end{equation}
  where $P$ is a manunally set probability and $N(t)$ is the number of type $t$ in those $n$ valid data points.

@@

  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
  \begin{algorithm}[tb]
    \caption{Neural Network Classification}\label{alg:NN}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
    \end{algorithmic}
  \end{algorithm}

@@

  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
    \caption{An example that multiple SVMs fail}
    \label{fig:SVM_fail}
  \end{figure}

  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\     
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $X$               & $X$        & $X$                   & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $X$               & $X$        & $X$                   & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}
